Component response rate variation drives stability in large complex systems

### 2018-05-22 SI.Rmd
Update SI

- [Code and simulations underlying Fig. 1](#Fig1) 
- [Code and simulations underlying Fig. 2](#Fig2) 
- [Stability across increasing $S$](#Incr_S}) 
- [Stability of ecological networks](#ecological) 
    - [Competitor networks](#competition) 
    - [Mutualist networks](#mutualism) 
    - [Predator-prey networks](#pred-prey) 
- [Feasilbility of complex systems](#Feasibility) 
- [Genetic algorithm](#ga)

@@

>>>>

- [Code and simulations underlying Fig. 1](#Fig1) 
- [Code and simulations underlying Fig. 2](#Fig2) 
- [Stability across increasing $S$](#Incr_S}) 
- [Stability of ecological networks](#ecological) 
    - [Competitor networks](#competition) 
    - [Mutualist networks](#mutualism) 
    - [Predator-prey networks](#pred-prey) 
- [Feasilbility of complex systems](#Feasibility) 
- [Different distributions of $\gamma$](#gam_dist)
- [Genetic algorithm](#ga)

@@

Different distributions of $\gamma$ {#gam_dist}
================================================================================
